---
title: "Republik Mailer"
author: "Salim Brüggemann"
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r, load-packages}
library(magrittr)
```

# Read in configuration

```{r, read-in-config}
if ( fs::file_exists("config.toml") )
{
  config <- RcppTOML::parseTOML(input = "config.toml",
                                escape = FALSE)
} else
{
  config <- list(from = "your.mail@address.suffix",
                 to = "your.mail@address.suffix",
                 salutation = "Ladies and gentleman",
                 greetings = "Einen schönen Tag wünscht  \nSalims MailBot \U1F916",
                 credits = paste("Dies ist eine automatisch generierte Nachricht.",
                                 "Der zugrundeliegende Code findet sich bei Interesse [hier](https://gitlab.com/salim_b/r/scripts/republik_mailer/)."),
                 default_formats = c("alles-was-recht-ist",
                                     "am-gericht",
                                     "briefing-aus-bern",
                                     "preis-der-republik"),
                 auth_cookie = "?")
}
```

# Define functions

## Knit `README.Rmd` to `README.md`

```{r, knit-readme}
knit_readme <- function(input = "README.Rmd",
                        output = "README.md")
{
  # knit Rmd to md
  knitr::knit(input = input,
              output = output,
              quiet = TRUE)

  # convert to custom Markdown format which prettifies the Markdown and is similar enough to
  # [GitLab Flavored Markdown](https://gitlab.com/help/user/markdown.md)
  rmarkdown::pandoc_convert(input = output,
                            output = output,
                            from = "markdown+emoji",
                            to = "markdown+emoji-simple_tables-multiline_tables-grid_tables-fenced_code_attributes-smart",
                            options = c("--atx-headers", "--columns=9999"))
}
```

## Get latest article metadata from specific Republik format

The code below fetches the link, title and lead of the latest articles from a specific article `format`, like
[Am Gericht](https://www.republik.ch/format/am-gericht) for example. You have to provide the value of the `connect.sid` cookie, either directly as
argument `auth_cookie` or in the configuration file `config.toml` in the working directory (recommended).

~~Note that the [cURL](https://curl.haxx.se/) command line tool must be available on the system.~~

```{r, get-latest-article-metadata}
get_latest_article_metadata <- function(format,
                                        auth_cookie = config$auth_cookie)
{
  # URL-decode `auth_cookie` if necessary
  if ( !stringr::str_detect(string = auth_cookie,
                            pattern = ":") )
  {
    auth_cookie %<>% xml2::url_unescape()
  }
  
  # COMMENTED OUT alternative way to fetch HTML using external curl CLI
  # do_repeat <- TRUE
  # counter <- 1L
  # 
  # while( do_repeat )
  # {
  #   # get HTML
  #   article_divs <-
  #     rlang::with_handlers(error = ~ rlang::abort(message = glue::glue("Can't fetch content from <https://www.republik.ch/format/{format}>!"),
  #                                                 parent = .),
  #                          system2(command = "curl",
  #                                  args = glue::glue("-v --cookie 'connect.sid={auth_cookie}' https://www.republik.ch/format/{format}"),
  #                                  stdout = TRUE,
  #                                  stderr = TRUE))
  #   
  #   curl_status_code <- attr(x = article_divs,
  #                            which = "status")
  #   
  #   # ensure curl exited with status `0` (success), otherwise try again 1 minute later
  #   if ( !is.null(curl_status_code) )
  #   {
  #     if ( counter < 10L )
  #     {
  #       rlang::warn(message = glue::glue("Curl failed to fetch content from <https://www.republik.ch/format/{format}> with exit status code ",
  #                                        "{curl_status_code}!\n For an overview of curl exit status codes, see ",
  #                                        "<https://curl.haxx.se/libcurl/c/libcurl-errors.html>.\n\nTrying again in 1 minute ..."))
  #       
  #       counter %<>% magrittr::add(1L)
  #       Sys.sleep(time = 60)
  #       
  #     } else
  #     {
  #       rlang::abort(message = glue::glue("Curl repeatedly failed to fetch content from <https://www.republik.ch/format/{format}>! ",
  #                                         "Last exit status code was {curl_status_code}!\nFor an overview of curl status codes, see ",
  #                                         "<https://curl.haxx.se/libcurl/c/libcurl-errors.html>."))
  #     }
  #     
  #   } else do_repeat <- FALSE
  # }
  # 
  # # extract relevant parts of HTML (aka "scraping")
  # response %<>%
  #   stringr::str_subset(pattern = "<body") %>%
  #   xml2::read_html() %>%
  #   # extract all <div> nodes that directly contain a <h1> node
  #   rvest::html_nodes(xpath = "//div[h1]")
  
  # fetch HTML (retry 10 times in increasing intervals in case of any error)
  ## initialize retry counter
  retry_counter <- 1L
  
  ## define custom error handler
  optimistic_error_handler <- function(error)
  {
    if ( retry_counter < 10 )
    {
      retry_counter <<- retry_counter + 1L
      Sys.sleep(time = 10 * retry_counter)
      fetch_html()
      
    } else
    {
      rlang::abort(message = glue::glue("Repeatedly failed to fetch content from <https://www.republik.ch/format/{format}>!"),
                   parent = error)
    }
  }
  
  ## define function to fetch HTML deploying above error handler
  fetch_html <- function() {
    
    rlang::with_handlers(httr::RETRY(verb = "GET",
                                     url = glue::glue("https://www.republik.ch/format/{format}"),
                                     httr::set_cookies(`connect.sid` = auth_cookie),
                                     times = 5L),
                         error = optimistic_error_handler)
  }
  
  ## fetch HTML at last
  response <- fetch_html()
  
  # test if authentication was successful
  if ( response %>%
       httr::content(as = "text") %>%
       stringr::str_detect(pattern = "Sie brauchen eine Mitgliedschaft, um die Beiträge zu lesen.") )
  {
    stop("Authentication failed which means the provided `auth_cookie` value is either wrong or expired! `auth_cookie` was set to:\n", auth_cookie)
  }
  
  # extract relevant parts of HTML (aka "scraping")
  response %<>%
    httr::content(as = "parsed") %>%
    rvest::html_node(css = "body") %>%
    # extract all <div> nodes that directly contain a <h1> node
    rvest::html_nodes(xpath = "//div[h1]")
  
  # ensure we actually got something
  if ( length(response) == 0 )
  {
    rlang::abort("No articles could be scraped! Maybe your `auth_cookie` is invalid?")
  }
  
  # extract article links and titles
  articles <-
    tibble::tibble(format =
                     format,
                   href =
                     response %>%
                     rvest::html_node(css = "h1") %>%
                     rvest::html_node(css = "a") %>%
                     rvest::html_attr(name = "href"),
                   title =
                     response %>%
                     rvest::html_node(css = "h1") %>%
                     rvest::html_text() %>%
                     stringr::str_trim())
  
  articles %<>% dplyr::mutate(
    # add article leads
    lead =
      glue::glue("//a[@href='{articles$href}']") %>%
      purrr::map(~ rvest::html_nodes(x = response,
                                     xpath = .x)) %>%
      purrr::map(rvest::html_text) %>%
      purrr::map(magrittr::extract, 2) %>%
      purrr::flatten_chr() %>%
      stringr::str_trim(),
    # make links absolute
    href = paste0("https://www.republik.ch", href)
  )
  
  articles
}
```

## Update local article metadata

```{r, update-local-article-metadata}
update_article_metadata <- function(formats = config$default_formats)
{
  # read in existing local metadata if possible
  if ( fs::file_exists("article_metadata.rds") )
  {
    article_metadata <<- readRDS(file = "article_metadata.rds")
    
  } else
  {
    article_metadata <<- tibble::tibble(format = character(0),
                                        href = character(0),
                                        title = character(0),
                                        lead = character(0),
                                        is_mailed = logical(0))
  }
  
  # update metadata
  article_metadata <<-
    formats %>%
    purrr::map_dfr(.f = get_latest_article_metadata) %>%
    dplyr::full_join(y = article_metadata,
                     by = colnames(.) %>% setdiff("is_mailed")) %>%
    tidyr::replace_na(replace = list(is_mailed = FALSE)) %>%
    # remove possible duplicates (keep latest metadata)
    dplyr::arrange(-dplyr::row_number()) %>%
    dplyr::filter(!duplicated(href)) %>%
    # sort tibble
    dplyr::arrange(format, href)
  
  article_metadata %>%
    readr::write_rds(path = "article_metadata.rds")
}
```

## Get new articles' `href`s

```{r, get-new-href}
get_new_hrefs <- function(format,
                          latest_one_only = FALSE)
{
  article_metadata %>%
    dplyr::filter(format == !!format) %>%
    dplyr::arrange(href) %>%
    purrr::when(latest_one_only ~ dplyr::filter(.data = ., dplyr::row_number() == nrow(.)),
                ~ .) %>%
    dplyr::filter(!is_mailed) %$%
    href
}
```

## Compose new articles

```{r, compose-new-articles}
compose_new_articles <- function(hrefs)
{
  article_metadata %>%
    dplyr::filter(href %in% hrefs) %>%
    dplyr::arrange(href) %$%
    glue::glue("[**{title}**]({href}){dplyr::if_else(is.na(lead), '', paste0('  \n', lead))}")
}
```

## Set `is_mailed`

```{r, set-mailed}
set_mailed <- function(mailed_hrefs)
{
  article_metadata <<-
    article_metadata %>%
    dplyr::mutate(is_mailed = dplyr::if_else(href %in% mailed_hrefs,
                                             TRUE,
                                             is_mailed))
  
  article_metadata %>%
    readr::write_rds(path = "article_metadata.rds")
}
```

## Insert CSS into blastula e-mail

```{r, insert-css-into-blastula}
insert_css_into_blastula <- function(blastula_email,
                                     css = "div.footer a {\n      color: #999999;\n    }")
{
  blastula_email$html_str %<>% stringr::str_replace(pattern = "(\\n +)(</style>)",
                                                    replacement = glue::glue("\\1{css}\\1\\2"))
  
  attrs <- attributes(blastula_email$html_html)
  blastula_email$html_html <- blastula_email$html_str
  attributes(blastula_email$html_html) <- attrs
  
  blastula_email
}
```

## Minify HTML

**Remarks:**

- These are simple wrapper functions around the CLI tool [minify](https://github.com/tdewolff/minify/tree/master/cmd/minify).
  Use parameter `command` to specify where its executable is found on your system (just leave it at its default `command = "minify"` if it's in the system's
  `$PATH`).

- Precompiled versions of minify can be downloaded [here](https://github.com/tdewolff/minify/releases). If you want or have to compile it yourself
  (e.g. for 32-bit plattforms), make sure the [Go distribution](https://golang.org/doc/install) and [Git](https://git-scm.com/downloads) are installed
  and run the following:

    ```sh
    go get -u -v github.com/tdewolff/minify/cmd/minify
    ```
    
    This installs/updates minify to your `$GOPATH`. To see where this is, run `go env GOPATH`.

```{r, minify-html}
minify_html <- function(html,
                        command = "minify")
{
  rlang::with_handlers(error = ~ rlang::abort(message = "HTML minification failed!",
                                              parent = .),
                       system2(command = fs::path_expand(command),
                               input = html,
                               args = "--type=html",
                               stdout = TRUE,
                               stderr = TRUE))
}
```

```{r, minify-html-file}
minify_html_file <- function(filepath,
                             command = "minify")
{
  filepath %>%
    fs::path_abs() %>%
    shQuote(type = "sh") %>%
    rep(times = 2) %>%
    paste0(collapse = " ") %>%
    paste("-o", .) %>%
    system2(command = fs::path_expand(command),
            args = .)
}
```

## Send E-Mail

This is a temporary replacement for `blastula::smtp_send()` until [issue #55](https://github.com/rich-iannone/blastula/issues/55) is fixed.

To set up [mailsend-go](https://github.com/muquit/mailsend-go/) on [RStudio Cloud](https://rstudio.cloud/), use:

```r
download.file(url = "https://github.com/muquit/mailsend-go/releases/download/v1.0.4/mailsend-go_1.0.4_linux-64bit.tar.gz",
              destfile = "m.tar.gz")
untar("m.tar.gz")
unlink("m.tar.gz)
```

Then use `send_mail(mailsend_cmd = "mailsend-go-dir/mailsend-go")`.

```{r, send-mail}
send_mail <- function(html_message_file,
                      subject,
                      to,
                      from,
                      creds_file,
                      mailsend_cmd = "mailsend-go",
                      quiet = TRUE)
{
  creds <- blastula::creds_file(file = creds_file)
  
  system2(command = mailsend_cmd,
          args = glue::glue(stringr::str_squish(paste0(
           dplyr::if_else(quiet, "-q ", ""),
           "-sub '{subject}' 
            -smtp '{creds['host']}' 
            -port {creds['port']} 
            auth 
            -user '{creds['user']}' 
            -pass '{creds['password']}' 
            -fname '{creds['sender_name']}' 
            -from '{from}' 
            -to '{to}' 
            body 
            -file '{html_message_file}'"))))
}
```

## Spread new articles

**Remarks:**

- Currently the package [blastula](https://rich-iannone.github.io/blastula/) used to send e-mails is undergoing heavy changes, i.a. the underlying program used
  for SMTP [is being replaced](https://rich-iannone.github.io/blastula/articles/sending_using_smtp.html#sending-email) by
  [mailsend-go](https://github.com/muquit/mailsend-go). Therefore you should use the development version installed directly from GitHub using:

    ```r
    remotes::install_github(repo = "rich-iannone/blastula")
    ```

- Beforehand you should [install mailsend-go](https://rich-iannone.github.io/blastula/articles/sending_using_smtp.html#installation-of-mailsend-go).

    On Debian/Ubuntu Linux you also have to install the Debian package `libsodium-dev` which is required by the R package `sodium`, which in turn is a
    dependency of the R package `keyring`, which is finally a dependency of the `blastula` R package.

- It's recommended to store the SMTP credentials to file. See the [README](README.md#-config) for details.

- It's recommended to assign the class `img-responsive` to images embedded in the mail text. Currently this _cannot_ be achieved by using Markdown
  (`![Alternative Text...](https://...)`). Instead you have to use plain HTML:

    ```html
    <img class='img-responsive' src='https://...' alt='Alternative Text...' />
    ```

```{r, spread-new-articles}
spread_new_articles <- function(format,
                                subject,
                                intro,
                                from = config$from,
                                to = config$to,
                                salutation = config$salutation,
                                greetings = config$greetings,
                                image_url = NULL,
                                image_text = "Symbolbild",
                                footer = config$credits,
                                latest_one_only = FALSE,
                                only_run_on_days = NULL)
{
  if ( !is.null(only_run_on_days) )
  {
    type_check <- only_run_on_days %>% purrr::map(.f = checkmate::check_int,
                                                  lower = 1,
                                                  upper = 7)
    
    if ( type_check %>%
         purrr::map_depth(.depth = 1,
                          .f = purrr::is_logical) %>%
         as.logical() %>%
         all() %>%
         not() )
    {
      stop(paste0("`only_run_on_days` must be an numeric vector containing weekday numbers between 1 and 7 (1 = monday, ... , 7 = sunday)!\n",
                  type_check %>% purrr::keep(.p = is.character) %>% purrr::flatten_chr() %>% paste0(collapse = "\n")))
    }
    
    if ( Sys.Date() %>%
         lubridate::wday(week_start = 1) %>%
         magrittr::equals(only_run_on_days) %>%
         any() )
    {
      spread(format = format,
             subject = subject,
             intro = intro,
             from = from,
             to = to,
             salutation = salutation,
             greetings =greetings ,
             image_url = image_url,
             image_text = image_text,
             footer = footer,
             latest_one_only = latest_one_only)
    }
  } else
  {
    spread(format = format,
           subject = subject,
           intro = intro,
           from = from,
           to = to,
           salutation = salutation,
           greetings =greetings ,
           image_url = image_url,
           image_text = image_text,
           footer = footer,
           latest_one_only = latest_one_only)
  }
}

spread <- function(format,
                   subject,
                   intro,
                   from,
                   to,
                   salutation,
                   greetings,
                   image_url,
                   image_text,
                   footer,
                   latest_one_only)
{
  # get hyperlinks of unmailed articles of desired format
  new_hrefs <-
    get_new_hrefs(format = format,
                  latest_one_only = latest_one_only) %>%
    purrr::when(length(.) == 0 ~ .,
                latest_one_only ~ dplyr::last(.),
                ~ .)
  
  if ( length(new_hrefs) > 0 )
  {
    # compose mail
    blastula::compose_email(
      body = paste0(
        "{salutation}\n\n{intro}\n\n",
        paste(compose_new_articles(hrefs = new_hrefs), collapse = "\n\n"),
        dplyr::if_else(!is.null(image_url),
                       glue::glue("\n\n\n<img class=\"img-responsive\" src=\"{image_url}\" alt=\"{image_text}\" />"),
                       ""),
        "\n\n", greetings),
      footer = footer,
      .title = subject) %>%
      insert_css_into_blastula() %$%
      html_str %>%
      # change mail background color to match Ubuntu GUI
      # TODO: use param `background_color` as soon as [PR #81](https://github.com/rich-iannone/blastula/pull/82) is merged
      stringr::str_replace_all(pattern = "(?i)#f6f6f6",
                               replacement = "#f2f1f0") %>%
      minify_html() %>%
      readr::write_file(path = "message.html")
    
    # send mail
    send_mail(html_message_file = "message.html",
              from = from,
              to = to,
              subject = subject,
              creds_file = ".smtp_credentials")
    
    # delete HTML message file
    fs::file_delete("message.html")
    
    # update `is_mailed` status
    set_mailed(mailed_hrefs = new_hrefs)
  }
}
```

### Alles was Recht ist

```{r, mail-alles-was-recht-ist}
mail_alles_was_recht_ist <- function(latest_one_only = TRUE)
{
  spread_new_articles(format = "alles-was-recht-ist",
                      subject = "\U2696\UFE0F Alles, was Recht ist in der Republik",
                      intro = "Heute ist ein neuer Beitrag in der Republik zu Recht und Justiz erschienen:",
                      image_url = "https://gitlab.com/salim_b/r/scripts/republik_mailer/raw/master/images/justitia-560.jpg",
                      latest_one_only = latest_one_only)
}
```

### Am Gericht (only on Wednesdays)

- Usually, a new article from this format is published on every Wednesday; set `only_run_on_days = 3` to restrict the function's execution to Wednesdays.

- Alternatiive (old) official symbolic picture for the format _Am Gericht_ is hosted here:
  <https://cdn.republik.space/s3/republik-assets/github/republik/format-am-gericht/images/ab46b8bfb396500f80893b333aece0419aa536ac.png?resize=560x>

```{r, mail-am-gericht}
mail_am_gericht <- function(only_run_on_days = NULL,
                            latest_one_only = TRUE)
{
  spread_new_articles(format = "am-gericht",
                      subject = "\U1F3DB\UFE0F Republik am Gericht",
                      intro = "Die Republik war wieder [am Gericht](https://www.republik.ch/format/am-gericht):",
                      image_url = paste0("https://cdn.repub.ch/s3/republik-assets/github/republik/format-am-gericht/images/",
                                         "d9d9981cc634153530bb57e0ccabc8d68cfbe726.png?resize=560x250"),
                      latest_one_only = latest_one_only,
                      only_run_on_days = only_run_on_days)
}
```

### Briefing aus Bern (only on Thursdays)

Usually, a new article from this format is published on every Thursday; set `only_run_on_days = 4` to restrict the function's execution to Thursdays

```{r, mail-briefing-aus-bern}
mail_briefing_aus_bern <- function(only_run_on_days = NULL,
                                   latest_one_only = TRUE,
                                   randomize_image = FALSE)
{
  if ( randomize_image )
  {
    # define random image choices
    images <- tibble::tibble(
      url = c("https://gitlab.com/salim_b/r/scripts/republik_mailer/raw/master/images/storm-brewing-over-the-parliament-560.jpg",
              "https://gitlab.com/salim_b/r/scripts/republik_mailer/raw/master/images/bundesplatz-560.jpg",
              "https://gitlab.com/salim_b/r/scripts/republik_mailer/raw/master/images/bundeshaus-560.jpg",
              "https://gitlab.com/salim_b/r/scripts/republik_mailer/raw/master/images/bundeshaus2-560.jpg",
              "https://gitlab.com/salim_b/r/scripts/republik_mailer/raw/master/images/water-fountain-560.jpg",
              "https://gitlab.com/salim_b/r/scripts/republik_mailer/raw/master/images/museumsnacht-bundeplatz-stereographic-560.jpg",
              "https://gitlab.com/salim_b/r/scripts/republik_mailer/raw/master/images/bern-bundesplatz-560.jpg"),
      credits = c(
        paste0(
          "_[Storm brewing over the Parliament](https://www.flickr.com/photos/chreegou/42317245170/)_ von Christian Scheidegger ",
          "ist lizenziert unter [CC-BY-SA 2.0](https://creativecommons.org/licenses/by-sa/2.0/)"),
        paste0(
          "_[Bundesplatz](https://www.flickr.com/photos/schoeband/6514744179/)_ von Andreina Schoeberlein ist lizenziert unter ",
          "[CC-BY-NC-ND 2.0](https://creativecommons.org/licenses/by-nc-nd/2.0/)"),
        paste0(
          "_[Bundeshaus](https://www.flickr.com/photos/twicepix/4450441204/)_ von Martin Abegglen ist lizenziert unter ",
          "[CC-BY-SA 2.0](https://creativecommons.org/licenses/by-sa/2.0/)"),
        paste0(
          "_[Bundeshaus](https://www.flickr.com/photos/twicepix/4875386468/)_ von Martin Abegglen ist lizenziert unter ",
          "[CC-BY-SA 2.0](https://creativecommons.org/licenses/by-sa/2.0/)"),
        paste0(
          "_[Water Fountain](https://www.flickr.com/photos/glodjib/7371568978/)_ von Guido Gloor Modjib ist lizenziert unter ",
          "[CC-BY-NC-ND 2.0](https://creativecommons.org/licenses/by-nc-nd/2.0/)"),
        paste0(
          "_[Museumsnacht Bundeplatz Stereographic](https://www.flickr.com/photos/habi/5546211688/)_ von David Haberthür ist lizenziert unter ",
          "[CC-BY-NC 2.0](https://creativecommons.org/licenses/by-nc/2.0/)"),
        paste0(
          "_[Bern Bundesplatz](https://www.flickr.com/photos/codeseven/3798802986/)_ von Philipp ist lizenziert unter ",
          "[CC-BY-NC-ND 2.0](https://creativecommons.org/licenses/by-nc-nd/2.0/)"))
    )
    
    # choose an image randomly
    random_image_choice <-
      runif(n = 1,
            min = 1,
            max = nrow(images)) %>%
      round(digits = 0)
    
    image_url <- images$url[random_image_choice]
    image_text <- images$credits[random_image_choice] %>% commonmark::markdown_text() %>% stringr::str_extract("^.+(?= von)")
    footer <- glue::glue("{images$credits[random_image_choice]}\n\n", config$credits)
    
  } else
  {
    image_url <- "https://cdn.repub.ch/s3/republik-assets/github/republik/magazine/images/175fcbe4fcb26c0cdcb31b62d6dae351345c16be.png?resize=560x360"
    image_text <- "Symbolbild"
    footer <- config$credits
  }
  
  # spread article
  spread_new_articles(format = "briefing-aus-bern",
                      subject = "\U1F1E8\U1F1ED Republik-Briefing aus Bern",
                      intro = paste("Das heutige [Briefing aus Bern](https://www.republik.ch/format/briefing-aus-bern) der Republik fasst",
                                    "_«das Wichtigste in Kürze aus Parlament, Regierung und Verwaltung, kurz: dem Bundeshaus»_",
                                    "der letzten 7 Tage zusammen:"),
                      image_url = image_url,
                      image_text = image_text,
                      footer = footer,
                      latest_one_only = latest_one_only,
                      only_run_on_days = only_run_on_days)
}
```

### Preis der Republik (only on Thursdays)

```{r, mail-preis-der-republik}
mail_preis_der_republik <- function(only_run_on_days = NULL,
                                    latest_one_only = TRUE)
{
  spread_new_articles(format = "preis-der-republik",
                      subject = "\U1F3C6 Preis der Republik",
                      intro = "Der allmonatliche [Preis der Republik](https://www.republik.ch/format/preis-der-republik) wurde soeben verliehen:",
                      image_url = paste0("https://cdn.repub.ch/s3/republik-assets/github/republik/format-preis-der-republik/images/",
                                         "bfd51622c2e607f006779492f542bca83942a56a.jpeg?resize=300x"),
                      latest_one_only = latest_one_only,
                      only_run_on_days = only_run_on_days)
}
```

### Loop

This is a very basic loop function intended to run the functions to spread new articles for an indefinite amount of time. Probably not what you want! 😉

```{r, loop}
loop <- function()
{
  while( TRUE )
  {
    # sleep until 6 in the morning
    lubridate::as_datetime(x = paste(Sys.Date() + ifelse(lubridate::hour(lubridate::as_datetime(Sys.time(),
                                                                                                tz = "Europe/Zurich")) < 6L,
                                                         0L,
                                                         1L),
                                     "06:00:00"),
                           tz = "Europe/Zurich") %>%
      magrittr::subtract(lubridate::as_datetime(x = Sys.time(),
                                                tz = "Europe/Zurich")) %>%
      hms::as.hms() %>%
      as.integer() %>%
      Sys.sleep()
    
    # then do your duty
    update_article_metadata()
    mail_alles_was_recht_ist()
    mail_am_gericht()
    mail_briefing_aus_bern()
    mail_preis_der_republik()
  }
}
```
