---
title: "«Republik am Gericht» Mailer"
author: "Salim Brüggemann"
date: "`r Sys.Date()`"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Requirements

First of all: This script doesn't allow any unauthenticated access to the online newspaper [Republik](https://www.republik.ch/)! You have to be a (paying) subscriber. This allows you to [log in to the site](https://www.republik.ch/anmelden) which results in the creation of a session cookie needed for authentication. This cookie is named `connect.sid`  and you need to provide its content[^view-cookie] (a cryptographic hash) as the `auth_cookie` argument to the function `get_latest_articles()`.


[^view-cookie]: How you access the locally stored cookies of a specific site in Google Chrome is described [here](https://developers.google.com/web/tools/chrome-devtools/storage/cookies), the same for Firefox [here](https://developer.mozilla.org/docs/Tools/Storage_Inspector). The cookie's content can also be stored in a text file named `.auth_cookie` in the same folder as this script.


# Define functions

## Get latest articles from specific Republik format

The code below fetches the link, title and lead of the latest articles from a specific article `format`, like [Am Gericht](https://www.republik.ch/format/am-gericht) for example.

```{r, get-latest-article-metadata}
get_latest_article_metadata <- function(format = "am-gericht",
                                        auth_cookie = NULL)
{
  # read in auth cookie from file
  if ( is.null(auth_cookie) )
  {
    if ( file.exists(".auth_cookie") )
    {
      auth_cookie <- readr::read_lines(file = ".auth_cookie",
                                       skip_empty_rows = TRUE,
                                       n_max = 1)
    } else
    {
      stop("No `auth_cookie` argument provided and no `.auth_cookie` file found either!")
    }
  }
  
  # COMMENTED OUT because auth doesn't work with httr::GET (why not?)
  # response <- httr::GET(url = glue::glue("https://www.republik.ch/format/{format}"),
  #                       httr::set_cookies(`connect.sid` = auth_cookie))
  #
  # alternative method to set cookies for httr (doesn't work either!)
  # httr::config(cookie = glue::glue("connect.sid={auth_cookie}"))
  #
  # test if authentication was successful
  # response %>%
  #   httr::content(as = "text") %>%
  #   stringr::str_detect(pattern = "Sie brauchen eine Mitgliedschaft, um die Beiträge zu lesen.",
  #                       negate = TRUE)
  
  article_divs <-
    system2(command = "curl",
            args = glue::glue("-v --cookie 'connect.sid={auth_cookie}' https://www.republik.ch/format/{format}"),
            stdout = TRUE,
            stderr = TRUE) %>%
    stringr::str_subset(pattern = "<body") %>%
    xml2::read_html() %>%
    # extract all <div> nodes that directly contain a <h1> node
    rvest::html_nodes(xpath = "//div[h1]")
  
  # ensure we actually got something
  if ( length(article_divs) == 0 )
  {
    stop("No articles could be scraped! Maybe your `auth_cookie` is invalid?",
         call. = FALSE)
  }
  
  # extract article links and titles
  articles <-
    tibble::tibble(format =
                     format,
                   href =
                     article_divs %>%
                     rvest::html_node(css = "h1") %>%
                     rvest::html_node(css = "a") %>%
                     rvest::html_attr(name = "href"),
                   title =
                     article_divs %>%
                     rvest::html_node(css = "h1") %>%
                     rvest::html_text())
  
  # add article leads
  articles %<>%
    dplyr::mutate(lead =
                    glue::glue("//a[@href='{articles$href}']") %>%
                    purrr::map(~ rvest::html_nodes(x = article_divs,
                                                   xpath = .x)) %>%
                    purrr::map(~ .x[2]) %>%
                    purrr::map(.f = rvest::html_text) %>%
                    purrr::flatten_chr())
  
  # make links absolute
  articles$href %<>% paste0("https://www.republik.ch", .)
  
  return(articles)
}
```

## Insert CSS into blastula e-mail

```{r, insert-css-into-blastula}
insert_css_into_blastula <- function(blastula_email,
                                     css = "div.footer a {\n      color: #999999;\n    }")
{
  blastula_email$html_str %<>% stringr::str_replace(pattern = "(\\n +)(</style>)",
                                                    replacement = glue::glue("\\1{css}\\1\\2"))
  
  attrs <- attributes(blastula_email$html_html)
  blastula_email$html_html <- blastula_email$html_str
  attributes(blastula_email$html_html) <- attrs
  
  return(blastula_email)
}
```

# Update local article metadata

```{r, store-article-metadata-locally}
# read in existing local metadata
if ( file.exists("article_metadata.rds") )
{
  article_metadata <- readRDS(file = "article_metadata.rds")
  
} else
{
  article_metadata <- tibble::tibble(format = character(0),
                                     href = character(0),
                                     title = character(0),
                                     lead = character(0),
                                     is_mailed = logical(0))
}

# update metadata
article_metadata %<>%
  dplyr::full_join(y = get_latest_article_metadata(format = "am-gericht"),
                   by = colnames(.) %>% setdiff("is_mailed")) %>%
  dplyr::full_join(y = get_latest_article_metadata(format = "briefing-aus-bern"),
                   by = colnames(.) %>% setdiff("is_mailed")) %>%
  tidyr::replace_na(replace = list(is_mailed = FALSE)) %>%
  # remove possible duplicates (keep latest metadata)
  dplyr::arrange(-dplyr::row_number()) %>%
  dplyr::filter(!duplicated(href))

saveRDS(object = article_metadata,
        file = "article_metadata.rds")
```

# Send e-mail with new articles

**Remarks:**

- Currently the package [blastula](https://rich-iannone.github.io/blastula/) used to send e-mails is undergoing heavy changes, i.a. the underlying program used for SMTP [is being replaced](https://rich-iannone.github.io/blastula/articles/sending_using_smtp.html#sending-email) by [mailsend-go](https://github.com/muquit/mailsend-go). Therefore you should use the development version installed directly from GitHub using:

    ```r
    remotes::install_github("rich-iannone/blastula")
    ```

- Beforehand you should [install mailsend-go](https://rich-iannone.github.io/blastula/articles/sending_using_smtp.html#installation-of-mailsend-go). On Ubuntu Linux, you also have to install the Debian package `libsodium-dev` which is required by the R package `sodium` which in turn is a dependency of the R package `keyring` which is finally a dependency of the `blastula` R package.

- It's recommended to create a file `.mail_credentials` containing the necessary authentication and connection information. You can create it using `blastula::create_email_creds_file()` like the following:

    ```r
    blastula::create_email_creds_file(user = "******@address.suffix",
                                      password = "******",
                                      host = "smtp.address.suffix",
                                      port = 587L,
                                      sender = "Your Name (\U1F916)",
                                      use_ssl = FALSE,
                                      use_tls = TRUE,
                                      authenticate = TRUE,
                                      creds_file_name = ".mail_credentials")
    ```

## Read in e-mail `from` address

```{r, read-in-sender-details}
from <- ifelse(file.exists(".from"),
               readr::read_lines(file = ".from",
                                 skip_empty_rows = TRUE,
                                 n_max = 1),
               "your.mail@address.suffix")
```

## Am Gericht

```{r, mail-articles-am-gericht}
if ( article_metadata %>%
     dplyr::filter(format == "am-gericht") %$%
     is_mailed %>%
     all() %>%
     not() )
{
  new_articles <-
    article_metadata %>%
    dplyr::filter(format == "am-gericht"
                  & !is_mailed) %>%
    dplyr::mutate(md = glue::glue("[**{title}**]({href})  \n{lead}")) %$%
    md
  
  blastula::compose_email(
    body = paste0(
      "Liebes C2D-Team,\n\nDie Republik war wieder [am Gericht](https://www.republik.ch/format/am-gericht):\n\n",
      paste(new_articles, collapse = "\n\n"),
      "\n\n![Symbolbild]",
      "(https://cdn.republik.space/s3/republik-assets/github/republik/format-am-gericht/images/ab46b8bfb396500f80893b333aece0419aa536ac.png?resize=516x)",
      "\n\nEinen schönen Tag wünscht  \nSalims MailBot \U1F916"),
    footer = paste0(
      "Dies ist eine automatisch generierte Nachricht. Der zugrundeliegende Code findet sich bei Interesse ",
      "[hier](https://gitlab.com/salim-b/republik_mailer).")) %>%
    insert_css_into_blastula() %>%
    blastula::smtp_send(from = from,
                        to = "c2d@zdaarau.ch",
                        subject = "\U2696\UFE0F Republik am Gericht \U2696\UFE0F",
                        creds_file = ".mail_credentials")
}
```

## Briefing aus Bern (only on Thursdays)

```{r, mail-articles-briefing-aus-bern}
if ( (article_metadata %>%
      dplyr::filter(format == "briefing-aus-bern") %$%
      is_mailed %>%
      all() %>%
      not()) &
     (Sys.Date() %>%
      lubridate::wday() %>%
      magrittr::equals(5)) )
{
  new_articles <-
    article_metadata %>%
    dplyr::filter(format == "briefing-aus-bern"
                  & !is_mailed) %>%
    dplyr::mutate(md = glue::glue("[**{title}**]({href})  \n{lead}")) %$%
    md
  
  if ( length(new_articles) > 1 )
  {
    stop("More than one new 'Briefing aus Bern' article found!")
  }
  
  images <- tibble::tibble(
    url = c("https://gitlab.com/salim-b/republik_mailer/raw/master/images/storm-brewing-over-the-parliament-516.jpg",
            "https://gitlab.com/salim-b/republik_mailer/raw/master/images/bundesplatz-516.jpg",
            "https://gitlab.com/salim-b/republik_mailer/raw/master/images/bundeshaus-516.jpg",
            "https://gitlab.com/salim-b/republik_mailer/raw/master/images/bundeshaus2-516.jpg",
            "https://gitlab.com/salim-b/republik_mailer/raw/master/images/water-fountain-516.jpg",
            "https://gitlab.com/salim-b/republik_mailer/raw/master/images/museumsnacht-bundeplatz-stereographic-516.jpg.jpg",
            "https://gitlab.com/salim-b/republik_mailer/raw/master/images/bern-bundesplatz-516.jpg"),
    credits = c(
      paste0(
        "_[Storm brewing over the Parliament](https://www.flickr.com/photos/chreegou/42317245170/)_ von Christian Scheidegger ist lizenziert unter ",
        "[CC-BY-SA 2.0](https://creativecommons.org/licenses/by-sa/2.0/)"),
      paste0(
        "_[Bundesplatz](https://www.flickr.com/photos/schoeband/6514744179/)_ von Andreina Schoeberlein ist lizenziert unter ",
        "[CC-BY-NC-ND 2.0](https://creativecommons.org/licenses/by-nc-nd/2.0/)"),
      paste0(
        "_[Bundeshaus](https://www.flickr.com/photos/twicepix/4450441204/)_ von Martin Abegglen ist lizenziert unter ",
        "[CC-BY-SA 2.0](https://creativecommons.org/licenses/by-sa/2.0/)"),
      paste0(
        "_[Bundeshaus](https://www.flickr.com/photos/twicepix/4875386468/)_ von Martin Abegglen ist lizenziert unter ",
        "[CC-BY-SA 2.0](https://creativecommons.org/licenses/by-sa/2.0/)"),
      paste0(
        "_[Water Fountain](https://www.flickr.com/photos/glodjib/7371568978/)_ von Guido Gloor Modjib ist lizenziert unter ",
        "[CC-BY-NC-ND 2.0](https://creativecommons.org/licenses/by-nc-nd/2.0/)"),
      paste0(
        "_[Museumsnacht Bundeplatz Stereographic](https://www.flickr.com/photos/habi/5546211688/)_ von David Haberthür ist lizenziert unter ",
        "[CC-BY-NC 2.0](https://creativecommons.org/licenses/by-nc/2.0/)"),
      paste0(
        "_[Bern Bundesplatz](https://www.flickr.com/photos/codeseven/3798802986/)_ von Philipp ist lizenziert unter ",
        "[CC-BY-NC-ND 2.0](https://creativecommons.org/licenses/by-nc-nd/2.0/)"))
  )
  
  random_image_choice <-
    runif(n = 1,
          min = 1,
          max = nrow(images)) %>%
    round(digits = 0)
  
  blastula::compose_email(
    body = paste0(
      "Liebes C2D-Team,\n\nDas heutige [Briefing aus Bern](https://www.republik.ch/format/briefing-aus-bern) der Republik fasst ",
      "_«das Wichtigste in Kürze aus Parlament, Regierung und Verwaltung, kurz: dem Bundeshaus»_ der letzten 7 Tage zusammen:\n\n",
      paste(new_articles, collapse = "\n\n"),
      "\n\n![Symbolbild]",
      "({images$url[random_image_choice]})",
      "\n\nEinen schönen Tag wünscht  \nSalims MailBot \U1F916"),
    footer = paste0(
      "{images$credits[random_image_choice]}\n\n",
      "Dies ist eine automatisch generierte Nachricht. Der zugrundeliegende Code findet sich bei Interesse ",
      "[hier](https://gitlab.com/salim-b/republik_mailer).")) %>%
    insert_css_into_blastula() %>%
    blastula::send_email_out(from = from,
                             to = "c2d@zdaarau.ch",
                             subject = "\U1F1E8\U1F1ED Republik-Briefing aus Bern \U1F1E8\U1F1ED")
}
```
